---
title: "Questionnaire Data Backward Mask Task"
output:
  html_document: 
    fig_height: 12
    fig_caption: yes
    fig_width: 8
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Library

```{r}
library(readxl)
library(rstatix)
library(ggplot2)
library(apaTables)
library(ez)
library(dplyr)
library(tidyr)
library(car)
library(emmeans)
library(ggplot2)
```

# Import Dataset

```{r}
data <- read_excel("Path/BackwardMask_Questionnaire_Results.xlsx", 
                 col_types = c("text", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", "numeric",  
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "text", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"), na = "na")

head(data)
```


# FB Analysis


## Rename Questionnaires 


```{r}

data <- data

colnames(data)[colnames(data) == "BDI-II Sum score"] ="BDI"
colnames(data)[colnames(data) == "BVAQ_New"] ="BVAQ"
colnames(data)[colnames(data) == "WMS Correct"] ="WMS"
colnames(data)[colnames(data) == "TM A"] ="TMT_A"
colnames(data)[colnames(data) == "TM B"] ="TMT_B"

colnames(data)[colnames(data) == "DERS_Gesamtwert"] ="DERS_sum_score"
colnames(data)[colnames(data) == "DERS_Nicht-Akzeptanz emotionalerReaktionen"] ="DERS_non_acceptance"
colnames(data)[colnames(data) == "DERS_Probleme mit zielorientiertem Verhalten"] ="DERS_goals"
colnames(data)[colnames(data) == "DERS_Impulskontrollprobleme"] ="DERS_impulse"
colnames(data)[colnames(data) == "DERS_Mangel an emotionaler Aufmerksamkeit"] ="DERS_awareness"
colnames(data)[colnames(data) == "DERS_Eingeschränkter Zugang zu Emotionsregulations-Strategien"] ="DERS_strategies"
colnames(data)[colnames(data) == "DERS_Mangel an emotionaler Klarheit"] ="DERS_clarity"

colnames(data)[colnames(data) == "CERQ_Selbstbeschuldigung"] ="CERQ_self_blame"
colnames(data)[colnames(data) == "CERQ_Akzeptanz"] ="CERQ_acceptance"
colnames(data)[colnames(data) == "CERQ_Rumination"] ="CERQ_rumination"
colnames(data)[colnames(data) == "CERQ_Positive Refokussierung"] ="CERQ_positive_reinforcement"
colnames(data)[colnames(data) == "CERQ_Refokussierung auf Planung"] ="CERQ_refocus_on_planning"
colnames(data)[colnames(data) == "CERQ_Positive Neubewertung"] ="CERQ_positive_reappraisal"
colnames(data)[colnames(data) == "CERQ_Relativieren"] ="CERQ_putting_into_perspective"
colnames(data)[colnames(data) == "CERQ_Katastrophisierung"] ="CERQ_catastrophizing"
colnames(data)[colnames(data) == "CERQ_Andere Beschuldigen"] ="CERQ_blaming_others"

colnames(data)[colnames(data) == "Hamilton Score"] ="Hamilton_Score"

colnames(data)[colnames(data) == "DigitSpan_Forwards_Span"] ="Digit_forward_span"
colnames(data)[colnames(data) == "DigitSpan_ForwardsTotal Score"] ="Digit_forward_score"
colnames(data)[colnames(data) == "DigitSpan_Backwards_Span"] ="Digit_backward_span"
colnames(data)[colnames(data) == "DigitSpan_Backwards_Total Score"] ="Digit_backward_score"
```

## look at dataset

```{r}
tibble(data)
```


## take only columns i need
# Transform data
```{r}

d_FB <- data[c('Group_MDD1_HC2', "BVAQ", "WMS", "TMT_A", "TMT_B", "STAI1", "STAI2",
             "DERS_sum_score", "DERS_non_acceptance", "DERS_goals", "DERS_impulse", "DERS_awareness", "DERS_strategies", "DERS_clarity",
             "CERQ_self_blame", "CERQ_acceptance", "CERQ_rumination", "CERQ_positive_reinforcement", "CERQ_refocus_on_planning",
             "CERQ_positive_reappraisal", "CERQ_putting_into_perspective", "CERQ_catastrophizing", "CERQ_blaming_others",
             "Digit_forward_span", "Digit_forward_score", "Digit_backward_span", "Digit_backward_score")]
```


## remove rows with missing values

```{r}
# Remove NA values from the dataset
data_FB_clean <- na.omit(d_FB)

# Check the dimensions of the cleaned dataset
dim(data_FB_clean)

# Use the cleaned dataset for further analysis

```


# Perform MANOVA

If you have multiple questionnaires and want to compare the sum scores between two groups while controlling for multiple comparisons, you can use a multivariate approach such as a multivariate analysis of variance (MANOVA) or a permutation-based approach.


```{r}
# Assuming 'manova_out' is the result object from your MANOVA analysis
manova_out <- manova(cbind(BVAQ, WMS, TMT_A, TMT_B, STAI1, STAI2,
                           DERS_sum_score, DERS_non_acceptance, DERS_goals, DERS_impulse, DERS_awareness, DERS_strategies, DERS_clarity,
                           CERQ_self_blame, CERQ_acceptance, CERQ_rumination, CERQ_positive_reinforcement, CERQ_refocus_on_planning,
                           CERQ_positive_reappraisal, CERQ_putting_into_perspective, CERQ_catastrophizing, CERQ_blaming_others,
                           Digit_forward_span, Digit_forward_score, Digit_backward_span, Digit_backward_score) 
                     ~ Group_MDD1_HC2,
                     data = data_FB_clean)
summary(manova_out, tol=0)

# Extract the dependent variable names
dependent_vars <- c("BVAQ", "WMS", "TMT_A", "TMT_B", "STAI1", "STAI2",
                    "DERS_sum_score", "DERS_non_acceptance", "DERS_goals", "DERS_impulse", "DERS_awareness", "DERS_strategies", "DERS_clarity",
                    "CERQ_self_blame", "CERQ_acceptance", "CERQ_rumination", "CERQ_positive_reinforcement", "CERQ_refocus_on_planning",
                    "CERQ_positive_reappraisal", "CERQ_putting_into_perspective", "CERQ_catastrophizing", "CERQ_blaming_others",
                    "Digit_forward_span", "Digit_forward_score", "Digit_backward_span", "Digit_backward_score")

```



```{r}
# Load required libraries
#library(tidyverse)
library(multcomp)

# Read the Excel sheet (assuming your data is in a sheet named "Sheet1")
data <- data_FB_clean
# Specify the questionnaire variables
dependent_vars <- c("BVAQ", "WMS", "TMT_A", "TMT_B", "STAI1", "STAI2",
                    "DERS_sum_score", "DERS_non_acceptance", "DERS_goals", "DERS_impulse", "DERS_awareness", "DERS_strategies", "DERS_clarity",
                    "CERQ_self_blame", "CERQ_acceptance", "CERQ_rumination", "CERQ_positive_reinforcement", "CERQ_refocus_on_planning",
                    "CERQ_positive_reappraisal", "CERQ_putting_into_perspective", "CERQ_catastrophizing", "CERQ_blaming_others",
                    "Digit_forward_span", "Digit_forward_score", "Digit_backward_span", "Digit_backward_score")

# Perform paired t-tests with Bonferroni correction
results <- purrr::map_df(dependent_vars, ~ {
  var_name <- as.character(.x)
  t_test_result <- t.test(data[[var_name]] ~ data$Group_MDD1_HC2, paired = FALSE)
  p_value <- t_test_result$p.value
  t_value <- t_test_result$statistic
  
  data.frame(
    Variable = var_name,
    P_Value = p_value,
    T_Value = t_value
  )
})

# Apply Bonferroni correction
results$Adjusted_P_Value <- p.adjust(results$P_Value, method = "bonferroni")

# Print the results table
print(results)

```


# Plot data

```{r}
data_FB_clean <- data_FB_clean %>%
  mutate(Group_MDD1_HC2 = as.factor(Group_MDD1_HC2))

#Reshape the data into long format 
d_FB_long <- data_FB_clean %>% gather(variable, value, -Group_MDD1_HC2)
```

```{r fig.width=11,fig.height=17}
# Create violin plots

ggplot(d_FB_long, aes(x = variable, y = value, fill = Group_MDD1_HC2)) +
  geom_violin(pattern = c("22", " ", " ")) +
  scale_fill_manual(values = c("gray", "white")) +
  facet_wrap(~variable, scales = "free", ncol = 4) +
  labs(x = "Variable", y = "Value") +
  theme_bw()
```

# Plot BDI

```{r}
data <- read_excel("C:/Users/juhoffmann/OneDrive - Uniklinik RWTH Aachen/Paper/fMRi/Analysis/BackwardMask_Questionnaire_Results.xlsx", 
                 col_types = c("text", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", "numeric",  
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "text", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"), na = "na")


colnames(data)[colnames(data) == "BDI-II Sum score"] ="BDI"

d_BDI <- data[c('Group_MDD1_HC2', "BDI")]
d_BDI <- na.omit(d_BDI)
d_BDI <- d_BDI %>%
  mutate(Group_MDD1_HC2 = as.factor(Group_MDD1_HC2))

```


```{r fig.width=2,fig.height=3}
# Create the violin plot

ggplot(d_BDI, aes(x = Group_MDD1_HC2, y = BDI, fill = Group_MDD1_HC2)) +
  geom_violin(data = subset(d_BDI, Group_MDD1_HC2 == "1"), fill = "grey") +
  geom_violin(data = subset(d_BDI, Group_MDD1_HC2 == "2"), fill = "white") +
  labs(x = "Group_MDD1_HC2", y = "BDI") +
  theme_bw()

```



```{r}
pairwise_results <- t.test(d_BDI$BDI ~ d_BDI$Group_MDD1_HC2, paired = FALSE)
pairwise_results
```

