---
title: "Mixed Model RT and Scores"
output:
  html_document:
    df_print: paged
---

This script estimates the effects of task and personality traits on the RT in the Backward Mask Priming task

## Import Packages

```{r}
library(lme4)         # mixed model package
library(lmerTest)     # library providing p-values for mixed models in lme4
library(readxl)       # read excel
library(ggplot2)      # graphics
library(emmeans)      # library for post-hoc tests
library(pbkrtest)     # needed for post-hoc tests in mixed models
library(jtools)       # post hoc tests
library(interactions) 
library(effects)      # estimate effects
library(apaTables)
library(dplyr)
library(tidyr)
library(readr)
library(afex)     
library(cowplot)
```

# Supplementary Model 4

## load dataset

```{r}
data <- read_excel("C:/Users/juhoffmann/Desktop/Git/UnconsciousBias/data/BackwardMask_Mean_RT_Long.xlsx", 
                 col_types = c("text", "text", "text", 
         "text", "text", "text", "numeric", 
         "numeric", "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "text", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"), na = "na")
head(data)
```

## rename columns

```{r}
colnames(data)[colnames(data) == "BVAQ_New"] ="BVAQ"
colnames(data)[colnames(data) == "BDI-II Sum score"] ="BDI"

colnames(data)[colnames(data) == "WMS Correct"] ="WMS"
colnames(data)[colnames(data) == "TM A"] ="TMT_A"
colnames(data)[colnames(data) == "TM B"] ="TMT_B"

colnames(data)[colnames(data) == "DERS_Gesamtwert"] ="DERS_sum_score"
colnames(data)[colnames(data) == "DERS_Nicht-Akzeptanz emotionalerReaktionen"] ="DERS_non_acceptance"
colnames(data)[colnames(data) == "DERS_Probleme mit zielorientiertem Verhalten"] ="DERS_goals"
colnames(data)[colnames(data) == "DERS_Impulskontrollprobleme"] ="DERS_impulse"
colnames(data)[colnames(data) == "DERS_Mangel an emotionaler Aufmerksamkeit"] ="DERS_awareness"
colnames(data)[colnames(data) == "DERS_Eingeschränkter Zugang zu Emotionsregulations-Strategien"] ="DERS_strategies"
colnames(data)[colnames(data) == "DERS_Mangel an emotionaler Klarheit"] ="DERS_clarity"

colnames(data)[colnames(data) == "CERQ_Selbstbeschuldigung"] ="CERQ_self_blame"
colnames(data)[colnames(data) == "CERQ_Akzeptanz"] ="CERQ_acceptance"
colnames(data)[colnames(data) == "CERQ_Rumination"] ="CERQ_rumination"
colnames(data)[colnames(data) == "CERQ_Positive Refokussierung"] ="CERQ_positive_reinforcement"
colnames(data)[colnames(data) == "CERQ_Refokussierung auf Planung"] ="CERQ_refocus_on_planning"
colnames(data)[colnames(data) == "CERQ_Positive Neubewertung"] ="CERQ_positive_reappraisal"
colnames(data)[colnames(data) == "CERQ_Relativieren"] ="CERQ_putting_into_perspective"
colnames(data)[colnames(data) == "CERQ_Katastrophisierung"] ="CERQ_catastrophizing"
colnames(data)[colnames(data) == "CERQ_Andere Beschuldigen"] ="CERQ_blaming_others"

colnames(data)[colnames(data) == "Hamilton Score"] ="Hamilton_Score"

colnames(data)[colnames(data) == "DigitSpan_Forwards_Span"] ="Digit_forward_span"
colnames(data)[colnames(data) == "DigitSpan_ForwardsTotal Score"] ="Digit_forward_score"
colnames(data)[colnames(data) == "DigitSpan_Backwards_Span"] ="Digit_backward_span"
colnames(data)[colnames(data) == "DigitSpan_Backwards_Total Score"] ="Digit_backward_score"
```

### Digit Span Info

Every item on Digit Span consists of two trials, each of which is scored 1 or 0 points. Pacing of the item stimuli is critical on Digit Span, as variations in how quickly or slowly they are provided can greatly impact item difficulty. The numbers are read at the rate of one per second, and there are a number of techniques that examiners use to establish an accurate, consistent pace.(<https://www.sciencedirect.com/science/article/pii/B9780124046979000029>) select important variables

```{r}
df <- data[c('Group_MDD1_HC2', "RT", "Gender_f1_m2", "name", "condition", "primer_emotion", "target_emotion",
            "congruence", "consciousness","Alter",
            "BVAQ", "WMS", "TMT_A", "TMT_B", "STAI1", "STAI2", "BDI",
             "DERS_sum_score", "DERS_non_acceptance", "DERS_goals", "DERS_impulse", "DERS_awareness", "DERS_strategies", "DERS_clarity",
             "CERQ_self_blame", "CERQ_acceptance", "CERQ_rumination", "CERQ_positive_reinforcement", "CERQ_refocus_on_planning",
             "CERQ_positive_reappraisal", "CERQ_putting_into_perspective", "CERQ_catastrophizing", "CERQ_blaming_others",
             "Digit_forward_span", "Digit_forward_score", "Digit_backward_span", "Digit_backward_score")]
```

## Drop NAs

```{r}
df %>% drop_na()
```

## Plot RT Density

```{r}
plot(density(df$RT),main="Density estimate of data")
```

```{r}
x <- df$RT
den <- density(x)
dat <- data.frame(x = den$x, y = den$y)

#Fit distributions
library(fitdistrplus)
fit.weibull <- fitdist(x, "weibull")
fit.normal <- fitdist(x,"norm")
fit.gamma <- fitdist(x, "gamma", lower = c(0, 0))

# Compare fits graphically
plot.legend <- c("Weibull", "Gamma","Normal")
par(mfrow = c(2, 2)) #show 4 pictures
denscomp(list(fit.weibull, fit.gamma, fit.normal), fitcol = c("red", "blue","green"), legendtext = plot.legend)
qqcomp(list(fit.weibull, fit.gamma, fit.normal), fitcol = c("red", "blue","green"), legendtext = plot.legend)
cdfcomp(list(fit.weibull, fit.gamma, fit.normal), fitcol = c("red", "blue","green"), legendtext = plot.legend)
ppcomp(list(fit.weibull, fit.gamma, fit.normal), fitcol = c("red", "blue","green"), legendtext = plot.legend)

```

Assume normal distribution

## factorize variables

```{r}
df$name                     <- factor(df$name, ordered = FALSE)
df$consciousness            <- factor(df$consciousness, ordered = FALSE)
df$congruence               <- factor(df$congruence, ordered = FALSE)
df$primer_emotion           <- factor(df$primer_emotion, ordered = FALSE)
df$target_emotion           <- factor(df$target_emotion, ordered = FALSE)
df$Gender_f1_m2             <- factor(df$Gender_f1_m2, ordered = FALSE)
df$Group_MDD1_HC2           <- factor(df$Group_MDD1_HC2, ordered = FALSE)
```

# Design Model

include all questionnaires as factor an check which questionnaire contributes to RT with the drop function (drop1(Model1, test="F"))

```{r}
Model.drop <- lmer(RT ~ 
                BVAQ + WMS + TMT_A + TMT_B + STAI1 + STAI2 + BDI
               + DERS_sum_score + DERS_non_acceptance + DERS_goals + DERS_impulse + DERS_awareness + DERS_strategies + DERS_clarity
               + CERQ_self_blame + CERQ_acceptance + CERQ_rumination + CERQ_positive_reinforcement + CERQ_refocus_on_planning
               + CERQ_positive_reappraisal + CERQ_putting_into_perspective + CERQ_catastrophizing + CERQ_blaming_others
               + Digit_forward_span + Digit_forward_score + Digit_backward_span + Digit_backward_score         
               + (1|name), data=df)
anova(Model.drop, type = 2, ddf= "Kenward-Roger")
```

```         
        + consciousness:congruence:Group_MDD1_HC2
           + consciousness:congruence:DERS_sum_score
           + consciousness:congruence:STAI1
           + consciousness:congruence:DERS_sum_score
           + consciousness:congruence:DERS_impulse 
```

```{r}
Model <- lmer(RT ~ consciousness*primer_emotion*Group_MDD1_HC2 
              + target_emotion*Group_MDD1_HC2 
              + Gender_f1_m2 
              + Alter # age
              + BDI
              + TMT_B
              + STAI2
              + DERS_sum_score
              + DERS_impulse 
              + DERS_goals
              + DERS_awareness
              + (1|name), data=df)
summary(Model)
```

```{r}
sjPlot:: tab_model(Model)
```

```{r}
sjPlot::plot_model(Model, type = "diag")
```

```{r}
anova.s <-anova(Model, type = 3, ddf= "Kenward-Roger")
print(anova.s)
```

## Post Hoc tests

```{r}
eff.primer        <- emmeans(Model, pairwise ~ primer_emotion)
eff.target        <- emmeans(Model, pairwise ~ target_emotion)
eff.gender        <- emmeans(Model, pairwise ~ Gender_f1_m2)
eff.consciousness <- emmeans(Model, pairwise ~ consciousness)
eff.BDI           <- cor.test(df$RT,df$BDI, method="spearman")
eff.TMT_B         <- cor.test(df$RT,df$TMT_B, method="spearman")
eff.DERS_sum      <- cor.test(df$RT,df$DERS_sum_score, method="spearman")
eff.DERS_impulse  <- cor.test(df$RT,df$DERS_impulse, method="spearman")
eff.DERS_awareness<- cor.test(df$RT,df$DERS_awareness, method="spearman")
eff.group_target  <- emmeans(Model, pairwise ~ Group_MDD1_HC2:target_emotion )
```

```{r}
eff.primer
eff.target
eff.gender 
eff.consciousness
eff.BDI
eff.TMT_B
eff.DERS_sum
eff.DERS_impulse
eff.DERS_awareness
eff.group_target
```

## Plot

```{r}
# Assuming you have a fitted model called "Model" and have extracted the coefficients
coefficients <- fixef(Model)

# Create a data frame with the coefficients and significance information
coef_df <- data.frame(
  Predictor = names(coefficients),
  Coefficient = coefficients,
  Significant = ifelse(p.adjust(coef(summary(Model))[, "Pr(>|t|)"], method = "holm") < 0.05, "*", "")
)

# Create a plot function for APA-style plots
apa_plot <- function(df) {
  ggplot(df, aes(x = reorder(Predictor, Coefficient), y = Coefficient)) +
    geom_bar(stat = "identity", fill = "blue", alpha = 0.7) +
    geom_text(aes(label = Significant), vjust = -0.5, size = 3.5) +
    labs(x = NULL, y = "Coefficient", title = "Significant Effects") +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(hjust = 0.5, size = 16)
    ) +
    coord_flip()
}

# Create APA-style plot
apa_plot(coef_df)
```

```{r}

primer <-  afex_plot(Model, x = "primer_emotion", 
            id = "name", dodge = 0.8, 
            data_geom = geom_violin, 
            mapping = c("linetype", "fill"),
            error_arg = list(width = 0.2),
            legend_title = "primer emotion",
            data_arg = list(width = 0.5)) + 
    ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("happy" = "greenyellow", "neutral" = "lightblue", "sad"= "orange")) + 
    theme(legend.position="none") +
  labs(y = "RT (in s)  ", x = "primer emotion")
  
target<-  afex_plot(Model, x = "target_emotion", 
            id = "name", dodge = 0.8,
            data_geom = geom_violin, 
            mapping = c("linetype", "fill"),
            error_arg = list(width = 0.2),
            data_arg = list(width = 0.5)) + ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("happy" = "greenyellow", "neutral" = "lightblue", "sad"= "orange")) +
    theme(legend.position="none") +
    labs(y = "RT (in s)  ", x = "target emotion")
  
conscious<-  afex_plot(Model, x = "consciousness", 
            id = "name", dodge = 0.8,
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            data_arg = list(width = 0.5)) + ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("conscious" = "grey", "unconscious" = "white")) +
    theme(legend.position="none") + 
    labs(y = "RT (in s)  ", x = "")
  
gender<-    afex_plot(Model, x = "Gender_f1_m2", #trace = "target_emotion", panel = "consciousness", 
            id = "name", dodge = 0.8,
            factor_levels = list(Gender_f1_m2 = c("female", "male")),
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            legend_title = "",
            data_arg = list(width = 0.5)) + ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("female" = "grey", "male" = "white")) +
    theme(legend.position="none") + 
    labs(y = "RT (in s)  ", x = "")
  
group_target<-  afex_plot(Model, x = "target_emotion", panel = "Group_MDD1_HC2", 
            id = "name", dodge = 0.8,
            factor_levels = list(Group_MDD1_HC2 = c("MDD", "HC"),
                                 target_emotion = c("h", "s", "n")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill", "group"), 
            error_arg = list(width = 0.2),
            legend_title = "",
            data_arg = list(width = 0.5)) + ggpubr::theme_pubr() +
    scale_fill_manual(values = c("h" = "greenyellow", "n" = "lightblue", "s"= "orange")) +
    theme(legend.position="none") + 
    labs(y = "RT (in s)", x = "")
```

```{r}
plot_bdi <- ggplot(df, aes(x = BDI, y = RT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubr() +
  labs(x = "BDI-II", y ="RT (in s)")

plot_tmt <- ggplot(df, aes(x = TMT_B, y = RT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubr() +
  labs(x = "TMT-B", y ="RT (in s)")

plot_ders_sum <- ggplot(df, aes(x = DERS_sum_score, y = RT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubr() +
  labs(x = "DERS sum score", y ="RT (in s)")

plot_ders_impulse <- ggplot(df, aes(x = DERS_impulse, y = RT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubr() +
  labs(x = "DERS impulse", y ="RT (in s)")

plot_ders_awareness<- ggplot(df, aes(x = DERS_awareness, y = RT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_pubr() +
  labs(x = "DERS awareness", y ="RT (in s)")
```

```{r}
# Combine plots into a grid
combined_plots <- cowplot::plot_grid(primer, target, conscious, gender, group_target,
                                     plot_bdi, plot_tmt, plot_ders_sum, plot_ders_impulse, plot_ders_awareness,
                            labels = c("A", "B", "C", "D","E","F","G","H","I","J"),
                            ncol = 2,nrow = 5)


ggsave("Path/GLMM_RT_FB.tiff", combined_plots, width = 8, height = 13)

print(combined_plots)
```

# Supplementary

## Model 5: Test if medication has an effect on RT values

```{r}
data <- read_excel("C:/Users/juhoffmann/Desktop/Git/UnconsciousBias/data/BackwardMask_Mean_RT_Long_MDD_On_vs_Off_Medication.xlsx", 
                 col_types = c("text", "numeric","text", "text", 
         "text", "text", "text", "numeric", 
         "numeric", "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "text", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"), na = "na")

head(data)
```

```{r}
df <- data[c("RT", "Gender_f1_m2", "name", "condition", "primer_emotion", "target_emotion", "congruence", "consciousness", "Alter", "Medication_1yes_2no")]
```

factorize variables

```{r}
df$name                     <- factor(df$name, ordered = FALSE)
df$consciousness            <- factor(df$consciousness, ordered = FALSE)
df$congruence               <- factor(df$congruence, ordered = FALSE)
df$primer_emotion           <- factor(df$primer_emotion, ordered = FALSE)
df$target_emotion           <- factor(df$target_emotion, ordered = FALSE)
df$Gender_f1_m2             <- factor(df$Gender_f1_m2, ordered = FALSE)
df$Medication_1yes_2no      <- factor(df$Medication_1yes_2no, ordered = FALSE)
```

estimate model

```{r}
Model5 <- lmer(RT ~ consciousness*primer_emotion
              + target_emotion
              + Gender_f1_m2 
              + Alter #age
              + Medication_1yes_2no
              + (1|name),
              data = df)
```

```{r}
sjPlot:: tab_model(Model5)
```

```{r}
sjPlot::plot_model(Model5, type = "diag")
```

```{r}
anova <-anova(Model5, type = 3, ddf= "Kenward-Roger")
print(anova)
```

## Model 6: Test if medication has an effect on N170 values

```{r}
data <- read_excel("C:/Users/juhoffmann/Desktop/Git/UnconsciousBias/data/erp_N170_MDD_On_vs_Off_Medication.xlsx")
head(data)
```

```{r}
# Factorise variables

data$mask[data$mask == "bewusst"] <- "conscious"
data$mask[data$mask == "unbewusst"] <- "unconscious"
data$name              <- factor(data$subName, ordered = FALSE)
data$consciousness     <- factor(data$mask, ordered = FALSE)
data$primer_emotion    <- factor(data$emotion, ordered = FALSE)
data$group             <- factor(data$group, ordered = FALSE)
data$gender            <- factor(data$Gender_f1_m2, ordered = FALSE)
data$Medication_1yes_2no  <- factor(data$Medication_1yes_2no, ordered = FALSE)
```

```{r}
Model6 <- lmer(N170 ~ consciousness*primer_emotion
                          + gender 
                          + age
                          + Medication_1yes_2no
                          + (1|name),
                          data=data)
```

```{r}
sjPlot::tab_model(Model6)
```

```{r}
sjPlot::plot_model(Model6, type = "diag")
```

```{r}
anova<-anova(Model6, type = 3, ddf= "Kenward-Roger")
print(anova)
```

## Model 7: Test if medication has an effect on N170/BOLD values

```{r}
data <- read_excel("C:/Users/juhoffmann/Desktop/Git/UnconsciousBias/data/regressors_10_Cluster_MixedModel_MDD_On_vs_Off_Medication.xlsx", col_types = c("numeric", "numeric", "text", "text", "numeric", "numeric", "numeric", "numeric", "numeric","numeric"))
head(data)
```

```{r}
data <- subset(data, Medication_1yes_2no != "NaN") 
```

Factorize variables

```{r}
data <- data%>%
  mutate(gender = as.factor(gender_f1_m2)) %>%
  mutate(group = as.factor(group_MDD1_HC2)) %>%
  mutate(emotion = as.factor(emotion)) %>%
  mutate(consciousness = as.factor(consciousness)) %>%
  mutate(cluster_number = as.factor(Cluster_number)) %>%
  mutate(Medication_1yes_2no = as.factor(Medication_1yes_2no))

```

```{r}
Model7 <- lmer(Cluster_value ~ emotion*consciousness + gender + cluster_number + Medication_1yes_2no
                       + (1|bids_number),
                       data = data)
```

```{r}
sjPlot::tab_model(Model7)
```

```{r}
anova<-anova(Model7, type = 3, ddf= "Kenward-Roger")
print(anova)
```


## Model 8: Test if Slope of N170 has an effect

```{r}
data <- read_excel("W:/Fmri_Forschung/Allerlei/JuliaS/GitHub/UnconsciousBias/data/updated_erp_N170_HC_and_MDD.xlsx")
```


```{r}
data$mask[data$mask == "bewusst"] <- "conscious"
data$mask[data$mask == "unbewusst"] <- "unconscious"
data$name              <- factor(data$subName, ordered = FALSE)
data$consciousness     <- factor(data$mask, ordered = FALSE)
data$primer_emotion    <- factor(data$emotion, ordered = FALSE)
data$group             <- factor(data$group, ordered = FALSE)
data$gender            <- factor(data$Gender_f1_m2, ordered = FALSE)
```

```{r}
Model8 <- lmer(N170 ~ consciousness*primer_emotion*group
                          + gender 
                          + age
                          + Slope
                          + (1|name),
                          data=data)
```

```{r}
sjPlot::tab_model(Model8)
```

```{r}
sjPlot::plot_model(Model8, type = "diag")
```

```{r}
anova<-anova(Model8, type = 3, ddf= "Kenward-Roger")
print(anova)
```
## Model 8a: Test if Slope of N170 has an effect + interaction effect
```{r}
data <- read_excel("W:/Fmri_Forschung/Allerlei/JuliaS/GitHub/UnconsciousBias/data/merged_N170_datasets_perBlock.xlsx")
```
```{r}
data$mask[data$mask == "bewusst"] <- "conscious"
data$mask[data$mask == "unbewusst"] <- "unconscious"
data$Block             <- factor(data$Block, ordered = FALSE)
data$name              <- factor(data$subName, ordered = FALSE)
data$consciousness     <- factor(data$mask, ordered = FALSE)
data$primer_emotion    <- factor(data$emotion, ordered = FALSE)
data$group             <- factor(data$group, ordered = FALSE)
data$gender            <- factor(data$Gender_f1_m2, ordered = FALSE)
```


```{r}
Model8.a.1 <- lmer(N170 ~ consciousness*primer_emotion*group
                          + gender 
                          + age
                          + Slope*primer_emotion*group
                          + (1|name),
                          data=data)
```
```{r}
anova<-anova(Model8.a.1, type = 3, ddf= "Satterthwaite")
print(anova)
```

```{r}
Model8.a.2 <- lmer(N170 ~ consciousness*primer_emotion*group
                          + gender 
                          + age
                          + Block
                          + Slope*primer_emotion*group
                          + (1|name),
                          data=data)
```
```{r}
anova<-anova(Model8.a.2, type = 3, ddf= "Satterthwaite")
print(anova)
```
```{r}
Model8.a.3 <- lmer(N170 ~ consciousness*primer_emotion*group
                          + gender 
                          + age
                          + Block*primer_emotion*group
                          + (1|name),
                          data=data)
```
```{r}
anova<-anova(Model8.a.3, type = 3, ddf= "Satterthwaite")
print(anova)
```

```{r}
anova(Model8.a.1,Model8.a.2, Model8.a.3)
```
-- Model 8.a.1. has slightly better AIC/BIC values

### get statistics of Model 8.a.1

```{r}
eff.consciousness <- emmeans(Model8.a.1, pairwise ~ consciousness)
eff.primer        <- emmeans(Model8.a.1, pairwise ~ primer_emotion,adjust ="bonferroni")
eff.gender        <- emmeans(Model8.a.1, pairwise ~ gender)
eff.age           <- cor.test(data$N170,data$age, method="spearman")
eff.group_consc   <- emmeans(Model8.a.1, pairwise ~ consciousness:group,adjust ="bonferroni")
```
```{r}
eff.consciousness
eff.primer     
eff.gender     
eff.age          
eff.group_consc
```
### plot effects of Model 8.a.1


```{r}
library(afex)     
library(cowplot)
#library(ggpubr)
```

```{r}
primer <-  afex_plot(Model8.a.1, x = "primer_emotion", 
            id = "name", dodge = 0.8, 
            factor_levels = list(primer_emotion = c("happy", "neutral","sad")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill"),
            error_arg = list(width = 0.2),
            legend_title = "primer emotion",
            data_arg = list(width = 0.5)) + 
    #ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("happy" = "greenyellow", "neutral" = "lightblue", "sad"= "orange")) + 
    theme(legend.position="none") +
    labs(y = "N170", x = "")

  
conscious<-  afex_plot(Model8.a.1, x = "consciousness", 
            id = "name", dodge = 0.8,
            factor_levels = list(consciousness = c("con", "uncon")),
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            data_arg = list(width = 0.5)) +# ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("con" = "grey", "uncon" = "white")) +
    theme(legend.position="none") + 
    labs(y = "N170", x = "")
  
gender<-    afex_plot(Model8.a.1, x = "gender", #trace = "target_emotion", panel = "consciousness", 
            id = "name", dodge = 0.8,
            factor_levels = list(gender = c("female", "male")),
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            legend_title = "",
            data_arg = list(width = 0.5)) + #ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("female" = "grey", "male" = "white")) +
    theme(legend.position="none") + 
    labs(y = "N170", x = "")

age<- ggplot(data, aes(x = age, y = N170)) +
  geom_point(size=0.4) +
  geom_smooth(method = "lm") +
  #ggpubr::theme_pubr() +
  theme_classic(base_size = 16) +
  labs(x = "", y ="N170")

con_in_group <-   afex_plot(Model8.a.1, x = "consciousness", panel = "group", 
            id = "name", dodge = 0.8,
            factor_levels = list(group = c("HC", "MDD"),
                                 consciousness = c("con", "uncon")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill", "group"), 
            error_arg = list(width = 0.1),
            legend_title = "",
            data_arg = list(width = 0.5)) + #ggpubr::theme_pubr() +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = c("con" = "grey", "uncon" = "white")) +
  theme(legend.position="none") + 
  geom_point(size=0.4)+
  labs(y = "N170", x = "")
```


```{r}
# Combine plots into a grid
combined_plots <- cowplot::plot_grid(primer, conscious, gender, age, con_in_group,
                            labels = c("A", "B", "C", "D", "E"),
                            ncol = 2,nrow = 4,
                            label_size = 15)

# Display the combined plots
#print(combined_plots)
ggsave("W:/Fmri_Forschung/Allerlei/JuliaS/Paper/2024_EEGfMRi/BiologicalPsychiatrySubmission/Revision2/GLMM_N170.tiff", combined_plots, width =7, height = 12)
```



## Model 8b: Test if Slope of N170 has an effect + interaction effect
```{r}
data <- read_excel("W:/Fmri_Forschung/Allerlei/JuliaS/GitHub/UnconsciousBias/data/merged_N170_datasets_10stacks.xlsx")
```
```{r}
data$mask[data$mask == "bewusst"] <- "conscious"
data$mask[data$mask == "unbewusst"] <- "unconscious"
data$name              <- factor(data$subName, ordered = FALSE)
data$consciousness     <- factor(data$mask, ordered = FALSE)
data$primer_emotion    <- factor(data$emotion, ordered = FALSE)
data$group             <- factor(data$group, ordered = FALSE)
data$gender            <- factor(data$Gender_f1_m2, ordered = FALSE)
```

```{r}
Model8.b <- lmer(N170 ~ consciousness*primer_emotion*group
                          + gender 
                          + age
                          + Slope*primer_emotion*group
                          + (1|name),
                          data=data)
```
```{r}
anova<-anova(Model8.b, type = 3, ddf= "Satterthwaite")
print(anova)
```

### get statistics of Model 8b

```{r}
eff.consciousness <- emmeans(Model8.b, pairwise ~ consciousness)
eff.primer        <- emmeans(Model8.b, pairwise ~ primer_emotion,adjust ="bonferroni")
eff.gender        <- emmeans(Model8.b, pairwise ~ gender)
eff.age           <- cor.test(data$N170,data$age, method="spearman")
eff.group_consc   <- emmeans(Model8.b, pairwise ~ consciousness:group,adjust ="bonferroni")
eff.group_primer  <- emmeans(Model8.b, pairwise ~ primer_emotion:group,adjust ="bonferroni")
eff.group_primer_con  <- emmeans(Model8.b, pairwise ~ consciousness:primer_emotion:group,adjust ="bonferroni")
```


```{r}
eff.consciousness
eff.primer     
eff.gender     
eff.age          
eff.group_consc
eff.group_primer  
eff.group_primer_con
```


### plot effects of Model 8b


```{r}
library(afex)     
library(cowplot)
#library(ggpubr)
```

```{r}
primer <-  afex_plot(Model8.b, x = "primer_emotion", 
            id = "name", dodge = 0.8, 
            factor_levels = list(primer_emotion = c("happy", "neutral","sad")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill"),
            error_arg = list(width = 0.2),
            legend_title = "primer emotion",
            data_arg = list(width = 0.5)) + 
    #ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("happy" = "greenyellow", "neutral" = "lightblue", "sad"= "orange")) + 
    theme(legend.position="none") +
    labs(y = "N170", x = "")

  
conscious<-  afex_plot(Model8.b, x = "consciousness", 
            id = "name", dodge = 0.8,
            factor_levels = list(consciousness = c("con", "uncon")),
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            data_arg = list(width = 0.5)) +# ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("con" = "grey", "uncon" = "white")) +
    theme(legend.position="none") + 
    labs(y = "N170", x = "")
  
gender<-    afex_plot(Model8.b, x = "gender", #trace = "target_emotion", panel = "consciousness", 
            id = "name", dodge = 0.8,
            factor_levels = list(gender = c("female", "male")),
            data_geom = geom_violin, 
            mapping = "fill",
            error_arg = list(width = 0.2),
            legend_title = "",
            data_arg = list(width = 0.5)) + #ggpubr::theme_pubr() + 
    theme_classic(base_size = 16) +
    geom_point(size=0.4) +
    scale_fill_manual(values = c("female" = "grey", "male" = "white")) +
    theme(legend.position="none") + 
    labs(y = "N170", x = "")

age<- ggplot(data, aes(x = age, y = N170)) +
  geom_point(size=0.4) +
  geom_smooth(method = "lm") +
  #ggpubr::theme_pubr() +
  theme_classic(base_size = 16) +
  labs(x = "", y ="N170")

con_in_group <-   afex_plot(Model8.b, x = "consciousness", panel = "group", 
            id = "name", dodge = 0.8,
            factor_levels = list(group = c("HC", "MDD"),
                                 consciousness = c("con", "uncon")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill", "group"), 
            error_arg = list(width = 0.1),
            legend_title = "",
            data_arg = list(width = 0.5)) + #ggpubr::theme_pubr() +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = c("con" = "grey", "uncon" = "white")) +
  theme(legend.position="none") + 
  geom_point(size=0.4)+
  labs(y = "N170", x = "")

emotion_in_group <-   afex_plot(Model8.b, x = "primer_emotion", panel = "group", 
            id = "name", dodge = 0.8,
            factor_levels = list(group = c("HC", "MDD"),
                                 primer_emotion = c("h", "n","s")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill", "group"), 
            error_arg = list(width = 0.1),
            legend_title = "",
            data_arg = list(width = 0.5)) + #ggpubr::theme_pubr() +
  theme_classic(base_size = 16) +
  scale_fill_manual(values = c("h" = "greenyellow", "n" = "lightblue", "s"= "orange")) +
  theme(legend.position="none") + 
  geom_point(size=0.4)+
  labs(y = "N170", x = "")


emotion_con_group <- afex_plot(Model8.b, x = "primer_emotion", panel = c("group", "consciousness"), 
            id = "name", dodge = 0.8,
            factor_levels = list(group = c("HC", "MDD"),
                                 primer_emotion = c("h", "n", "s"),
                                 consciousness = c("con", "uncon")),
            data_geom = geom_violin, 
            mapping = c("linetype", "fill", "group"), 
            error_arg = list(width = 0.1),
            legend_title = "",
            data_arg = list(width = 0.5)) + 
  theme_classic(base_size = 12) +
  scale_fill_manual(values = c("h" = "greenyellow", "n" = "lightblue", "s" = "orange")) +
  theme(legend.position = "none") + 
  geom_point(size = 0.4) +
  labs(y = "N170", x = "")
```

```{r}
# Combine plots into a grid
combined_plots <- cowplot::plot_grid(primer, conscious, gender, age, con_in_group, emotion_in_group, emotion_con_group,
                            labels = c("A", "B", "C", "D", "E", "F", "G"),
                            ncol = 2,nrow = 4,
                            label_size = 15)

# Display the combined plots
#print(combined_plots)
ggsave("W:/Fmri_Forschung/Allerlei/JuliaS/Paper/2024_EEGfMRi/BiologicalPsychiatrySubmission/Revision2/GLMM_N170.tiff", combined_plots, width =7, height = 12)

```

## Model 9: Effect of Demographics on Neurophysiological data


Gender: 2=men, 1=women

```{r}
data <- read_excel("C:/Users/juhoffmann/Desktop/Git/UnconsciousBias/data/erp_N170_HC_and_MDD.xlsx")
head(data)
```

```{r}
data$mask[data$mask == "bewusst"] <- "conscious"
data$mask[data$mask == "unbewusst"] <- "unconscious"
data$name              <- factor(data$subName, ordered = FALSE)
data$consciousness     <- factor(data$mask, ordered = FALSE)
data$primer_emotion    <- factor(data$emotion, ordered = FALSE)
data$group             <- factor(data$group, ordered = FALSE)
data$gender            <- factor(data$Gender_f1_m2, ordered = FALSE)
```

```{r}
Model9 <- lmer(N170 ~ gender*group + age*group
              + (1|name),
              data=data)
```

```{r}
anova<-anova(Model9, type = 3, ddf= "Kenward-Roger")
print(anova)
```
